Pre-/Post-Trikafta (Prospective)

### 2022-02-15 Christine Chan/Pre-post Trikafta Prospective/pre_post_trikafta_prospective_analysis.Rmd
Update pre_post_trikafta_prospective_analysis.Rmd

@@

p <- paired(f,data = df, id = Study.ID)

@@

```{r}
for (v in t2_vars) {
  v = gsub("`","",v)
  if(is.numeric(df[,v])){
    print(hist(df[,v]))
  } else {
    kable(table(df[,v]))
  }
}
```

>>>>

df$Group = factor(df$Group,levels = c("NGT","AGT","CFRD"),ordered = T)

@@

p <- paired(f,data = df, id = Study.ID,numeric.test = "signed.rank",signed.rank.exact = F)

@@

Group was treated as an ordered variable with NGT < AGT < CFRD.
